  1. `r data_muddy_episodes_centroids_intersection[[1]]`: 02-010-2015 (episode that was recoded as the data for
  2015 and future didnt check out with this one), seems to be exactly the same episode as 06-024. I will remove
  02-010-2015 as it is redundant.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[2]]`: 02-037 and 02-038 are the same
  episode duplicated. I maintain 02-037.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[2]], data_muddy_deboscat_centroids)
```
  
  1. `r data_muddy_episodes_centroids_intersection[[3]]`: 04-036 for 2017 (which was deemed as no fix for the
  new or error category) seems to be exactly the same as 04-004. I will remove this year from 04-036.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[3]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[4]]`: Similar as before. But in this case is the 04-005 for
  2017 and 2018 that seems to represent 04-036 in 2017. I will change this.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[4]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[5]]`: Here is strange. It seems like 04-031 from 2016 to
  2018 is the continuation of 04-026. I will change this.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[5]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[6]]`: 04-038 seems to be the same as 04-033. It only exist
  one year (2016) and is the same as 04-033. I will remove this one.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[6]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[7]]`: 04-040, new episode after several years in the same
  place as 04-014. No fix here.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[7]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[8]]`: 04-029 and 04-048 new episode after several
  years in the same place as 04-029. No fix here.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[8]], data_muddy_deboscat_centroids)
```
  
  1. `r data_muddy_episodes_centroids_intersection[[9]]`: 06-006 and 06-007. They are the same episode, but
  separated only for 2012. I'm gonna union the polygons for that year. The values, I maintain the same, because
  the mean is really similar.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[9]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[10]]`: 06-008 and 06-015. I don't understand why they
  are different episodes, but I'm not gonna fix it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[10]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[11]]`: 06-010 and 06-018. 06-018 is crazy, it is dancing
  around 06-010. Why they are different episodes is above my pay grade. No fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[11]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[12]]`: 06-060 seems the union of 06-010 and 06-018, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[12]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[13]]`: A different episode years after, no fix here
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[13]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[14]]`: Episodes evolving, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[14]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[15]]`: 06-060 seems the union of 06-010 and 06-018 and 06-016, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[15]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[18]]`: 06-020 is new in 2022 (after two
  years). Fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[18]], data_muddy_deboscat_centroids)
```

1. `r data_muddy_episodes_centroids_intersection[[21]]`: 06-020 is new in 2022 (after two
  years). Fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[21]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[22]]`: 07-026 seems the continuation of 07-019 from 2020 to now,
  fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[22]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[23]]`: 10-004 polygon for 2015 is wrong, fix it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[23]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[24]]`: episode fagociting another, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[24]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[25]]`: 10-040 is exactly the same as 19-040. Remove it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[25]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[26]]`: 10-046 is exactly the same as 19-046. Remove it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[26]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[27]]`: 13-004 in 2022 must be a new, but only if fullfill the checks
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[27]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[28]]`: 14-007 and 14-034 reappear in 2022, no fix here.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[28]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[29]]`: 14-066 for 2020 is really 14-013, fix it. Also, in 2021 and 2022 remove 14-066.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[29]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[30]]`: What??, and see `r data_muddy_episodes_centroids_intersection[[33]]`
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[30]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[31]]`: Really??, 2 episodes?? No fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[31]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[32]]`: Change all 14-078
  to 14-059
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[32]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[33]]`: Really?? and see `r data_muddy_episodes_centroids_intersection[[30]]`. It seems like the 2017 is a mix of the three, who knows.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[33]], data_muddy_deboscat_centroids)
create_polygon_plot_2(
  c(data_muddy_episodes_centroids_intersection[[30]], data_muddy_episodes_centroids_intersection[[33]]),
  data_muddy_deboscat_centroids
)
```

  1. `r data_muddy_episodes_centroids_intersection[[35]]`: 14-078 dance around 14-075 along the years, yujuu!.
  No fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[35]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[36]]`: 16-002 for 2014 is a copy of 16-003, remove it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[36]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[37]]`: 19-013 reappears, but broken into 19-13 and 19-111
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[37]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[38]]`: 19-035 reappears, but as 19-112
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[38]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[39]]`: 19-036 reappears, but as 19-113
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[39]], data_muddy_deboscat_centroids)
```
  
  1. `r data_muddy_episodes_centroids_intersection[[40]]`: 19-002 is broken in two parts in 2016, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[40]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[42]]`: 20-012-2012 is really 20-005, fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[42]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[42+1]]`: Let's broke the episodes in pieces!! No fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[42+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[43+1]]`: 21-031-2020 in 2018 (only year available for this episode)
  is in reality 24-031. Fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[43+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[44+1]]`: New episode after years, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[44+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[45+1]]`: 38-002 in 2012 is a duplicated of 23-002. Also,
  38-002 in 2015 is wrong and is again 23-002. Fix it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[45+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[46+1]]`: 23-010 and 23-011 must be new. Fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[46+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[47+1]]`: 24-001 in 2012 is really 24-032. Fix it. 24-032 should be a new in 2022.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[47+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[48+1]]`: 24-016 in 2019 is really 24-106. Fix it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[48+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[49+1]]`: Two different episodes, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[49+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[50+1]]`: 2Two different episodes, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[50+1]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[51+2]]`: 24-043 in 2012 is a duplicated of 24-044, remove
  it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[51+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[52+2]]`: Not sure what happened here, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[52+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[53]]`: Not sure what happened here, no fix.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[53]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[54]]`: 24-073-2015 is a duplicated of 24-064, remove it. 24-064 in 2022 new one
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[54]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[55]]`: 24-073 in 2022 is new
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[55]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[56]]`: Different episodes after years, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[56]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[57]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[57]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[58]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[58]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[59]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[59]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[58+2]]`: 25-037-2016 is the same as 25-029, change it.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[58+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[59+2]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[59+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[62]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[62]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[63]]`: Different episodes, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[63]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[64]]`: 27-001 in 2017 is in reality 28-001. Fix it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[64]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[65]]`: No idea, no fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[65]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[66]]`: 31-001-2012 is in reality 31-007-2015
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[66]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[67]]`: 31-007-2012 is in reality 31-001-2015
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[67]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[68]]`: 31-002-2012 is in reality 31-008-2016
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[68]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[69]]`: 31-008-2012 is in reality 31-002-2015
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[69]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[68+2]]`: Different episodes in different years
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[68+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[69+2]]`: 31-005 in 2022 sh
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[69+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[72]]`: Different episodes in different years.
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[72]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[73]]`: Different episodes after one year??? No fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[73]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[74]]`: No fix
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[74]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[77]]`: Another classic, dancing episodes, come and see!!
  32-011 for 2014, remove it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[77]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[78]]`: 32-013 seems to be 32-017
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[78]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[79]]`: Different episodes
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[79]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[78+2]]`: Different episodes after years
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[78+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[79+2]]`: Different episodes after years. 34-051 is new in 2022
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[79+2]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[82]]`: 35-012 is in reality 35-013, duplicated, remove it
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[82]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[83]]`: 36-032 is in reality 35-032
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[83]], data_muddy_deboscat_centroids)
```


  1. `r data_muddy_episodes_centroids_intersection[[84]]`: 35-039 new episode
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[84]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[86]]`: 40-003-2012 is in reality 40-006
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[86]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[87]]`: No idea, remove 40-005
  
```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[87]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[88]]`: 40-018 seems to be part of the old 40-003, so I
  dont do anything.

```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[88]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[89]]`: 40-019 seems to be part of the old 40-003, so I
  dont do anything, as before

```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[89]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[89]]`: Change of county?? No fix

```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[89]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[90]]`: New episode after years

```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[90]], data_muddy_deboscat_centroids)
```

  1. `r data_muddy_episodes_centroids_intersection[[90]]`: New episode after years

```{r}
create_polygon_plot_2(data_muddy_episodes_centroids_intersection[[90]], data_muddy_deboscat_centroids)
```
