---
title: "DBC data cleaning"
author: "Víctor Granda"
date: "03/06/2023"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    theme: journal
    df_print: tibble
  pdf_document: 
    toc: yes
    toc_depth: 4
    number_sections: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Libraries and functions

```{r libraries_and_functions}
# libraries
library(tidyverse)
library(sf)
library(glue)
# functions
source('helper_functions_for_cleaning.R')
# counties
counties_sf <-
  sf::read_sf('../../../01_nfi_app/nfiApp/data-raw/shapefiles/bm5mv20sh0tpc1_20180101_0.shp') %>%
  dplyr::select(spatial_county_id = CODICOMAR, spatial_county_name = NOMCOMAR)
```


# Initializing the data


## 2011 starting point

We will use the 2011 data just to get the code of the episodes started that
year. Data from this year is not usable.

```{r 2011_episodes}
data_raw_2011 <- read_csv2('dbc11.csv') %>%
  mutate(
    episode_id = str_extract(codi, "^\\d{2}-\\d{3}"),
    geometry = sf::st_as_sfc(lapply(.$areaafectada, sf:::hex_to_raw), EWKB = TRUE),
    year = 2011
  ) %>%
  select(episode_id, geometry, year)

episodes_existing_in_2011 <- data_raw_2011 %>% pull(episode_id) %>% unique()
```

## 2012 and 2013

Data from 2012 and 2013 lack of percentages for affectations, but we decide to
consider a new event when there is mortality and the afected percentage is equal or above
5% and/or there are decoloration and/or defoliation and the affected percentage
is equal or above 50%.

### Data loading and preliminary cleaning

We need to load the data, name the variables and convert healthy trees percentage
(`arbre`) in `affected_trees_percentage` ($100 - arbre$)

```{r}
data_raw_2012_2013 <-
  readr::read_csv2('dbc12_13.csv') %>%
  # separate episode id from the year
  tidyr::separate(
    col = codi, into = c("episode_id", "year"), sep = 6
  ) %>%
  # remove especial year codes and convert to numeric with full year number
  # obtain the year from the sampling date and use it
  dplyr::mutate(
    year = stringr::str_remove_all(year, '[-abcde]'),
    year = as.numeric(year) + 2000,
    arbre = 100 - arbre,
    areaafectada = sf::st_as_sfc(lapply(.$areaafectada, sf:::hex_to_raw), EWKB = TRUE)
  ) %>% {
    data_year_check <- .
    message(glue::glue("Are all years in 2012 or 2013?: {all(data_year_check$year %in% c(2012, 2013))}"))
    data_year_check
  } %>%
  # renaming vars
  dplyr::rename(
    geometry = areaafectada,
    species_id = nomespecie,
    affected_trees_perc = arbre,
    affected_trees_distribution = distribucio,
    cover_perc = recobriment
  )
```

## 2014 : 2020

#### Data pre-preparation

Data from 2014 and following years is in the same table. Let's prepare the table to
work with it:


```{r 2014_2020_data}
data_raw_2014_2020 <-
  readr::read_csv2(
    'dbc14_20.csv'
  ) %>%
  # convert to numeric
  dplyr::mutate(
    dplyr::across(.cols = c(recobriment, dplyr::ends_with('perc')), .fns = as.numeric)
  ) %>%
  # separate episode id from the year
  tidyr::separate(
    col = codi, into = c("episode_id", "year_id"), sep = 6
  ) %>%
  # remove especial year codes and convert to numeric with full year number
  # obtain the year from the sampling date and use it
  dplyr::mutate(
    year_id = stringr::str_remove_all(year_id, '[-abcde]'),
    year_id = as.numeric(year_id) + 2000,
    year = lubridate::year(dataobservacio),
    year = if_else(year < 1021, year+1000, year),
    year = if_else(year == 2106, 2016, year),
  )

year_mismatch <- data_raw_2014_2020 %>%
  filter(year_id != year) %>%
  select(episode_id, year_id, year, dataobservacio)

# look carefully
data_raw_2014_2020 %>%
  dplyr::filter(episode_id %in% unique(year_mismatch[['episode_id']])) %>%
  dplyr::arrange(episode_id, year_id, year)
```

##### '20-014'

In the "20-014" episode for 2018, there is no polygon, only data, so this episode has an area of zero.
We are gonna take the 2019 polygon to use it

```{r fix20014}
data_raw_2014_2020[which(data_raw_2014_2020$episode_id == '20-014' & data_raw_2014_2020$year == 2018), 'areaafectada'] <-
  data_raw_2014_2020[which(data_raw_2014_2020$episode_id == '20-014' & data_raw_2014_2020$year == 2019), 'areaafectada']
```

##### 06, 31 and 32 counties

These counties are really really bad. So, that after running this for the first time we decided to remove
them from the final table. Now, Mireia has done an amazing archeological work to save the most of them. But
we need to apply some changes to them prior to use them. Lets do that here (even if that will affect also
to the 2012-2013 data). For that there is an script that we will run:

```{r fix_06_31_32}
source('fix_06_31_32.R')
```


##### Year mismatches

Some episodes (`r length(unique(year_mismatch[['episode_id']]))`) for some years have a mismatch between the
year in the code and the year in the sampling date. We check those to see what happened:

  - "06-024", "13-001", "13-002", "14-023", "14-074", "20-009", "20-011", "24-112", "25-007",
    "25-022", "25-031", "31-008", "35-010": Trust the sampling date
  - "14-013": Strange case. It seems that 2018 is coded twice with errors, but duplicated. I will remove
    the duplicate as the values are identical
  - "14-015": Same as before for 2018. So I will remove the duplicate as the values are identical
  - "24-078": Data for 2014 is really duplicated data from 2016 due to error in input, I will remove the
    2014 data
  - "15-004", "15-008", "16-001": Error is in previous dates (before 2014)


Also, as we fix the year mismatches and the '20-014', we will pre clean the raw data:

```{r year_mismatches_fix}
data_dirty_2014_2020 <-
  data_raw_2014_2020 %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name %in% c("14-013", "14-015")) {
        res <- episode_data %>%
          dplyr::filter(as.character(dataobservacio) != "2017-09-29")
      } else {
        if (episode_name == "24-078") {
          res <- episode_data %>%
            dplyr::filter(year != 2014)
        } else {
          res <- episode_data
        }
      }
      return(res)
    }
  ) %>%
  # filter years before 2014 and remove "cicatrizats"
  dplyr::filter(
    year > 2013,
    nouoantic != 'C'
  ) %>%
  # final names
  dplyr::rename(
    geometry = areaafectada,
    # affectation_type = tipusafectacio,
    new_episode = nouoantic,
    affected_trees_type = arbresnousafectats,
    affected_trees_distribution = distribucio,
    species_id = nomespecie,
    cover_perc = recobriment,
    affected_trees_perc = arbres_afectats_perc,
    mortality_perc = mortalitat_perc,
    defoliation_perc = defoliacio_perc,
    decoloration_perc = decoloracio_perc
  ) %>%
  # get the geometry in the correct format, calculate episode area and tranform year to integer
  dplyr::mutate(
    geometry = sf::st_as_sfc(lapply(.$geometry, sf:::hex_to_raw), EWKB = TRUE),
    episode_area = as.numeric(sf::st_area(geometry)/10000),
    year = vctrs::vec_cast(year, integer())
  ) %>%
  # reorganizing variables
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area,
    dplyr::everything(), -tipusafectacio, -year_id, -dataobservacio
  )
```


## 2021 data (update Novemeber 2021)

We need to create the 2021 raw data and perform the cleaning process

```{r data_raw_2021}
data_raw_2021 <-
  readr::read_csv2('dbc21.csv') %>%
  # convert to numeric
  dplyr::mutate(
    dplyr::across(.cols = c(recobriment, dplyr::ends_with('perc')), .fns = as.numeric)
  ) %>%
  # separate episode id from the year
  tidyr::separate(
    col = codi, into = c("episode_id", "year_id"), sep = 6
  ) %>%
  # fix episode code in worng ones
  dplyr::mutate(
    episode_id = dplyr::case_when(
      episode_id == "40-14-" ~ "40-014",
      episode_id == "40-15-" ~ "40-015",
      episode_id == "40-16-" ~ "40-016",
      episode_id == "40-19-" ~ "40-019",
      TRUE ~ episode_id
    )
  ) %>% 
  # remove especial year codes and convert to numeric with full year number
  # obtain the year from the sampling date and use it
  dplyr::mutate(
    year_id = stringr::str_remove_all(year_id, '[-abcde]'),
    year_id = as.numeric(year_id) + 2000,
    year = lubridate::year(dataobservacio),
    year = if_else(year < 1021, year+1000, year),
    year = if_else(year == 2106, 2016, year),
  )

year_mismatch <- data_raw_2021 %>%
  filter(year_id != year) %>%
  select(episode_id, year_id, year, dataobservacio)
```

Now we have the raw data, is time to create the dirty one. In 2021 there are problems with "10" county
episodes. Some of them are missing the complete episode code (i.e. "10-13-" instead of "10-013"). We
need to fix that here also.

```{r data_dirty_2021}
episode_id_10_county_fix <- function(episode_id) {
  if (episode_id %in% c("10-13-", "10-14-", "10-15-", "10-16-", "10-17-", "10-19-")) {
    return(paste0("10-0", stringr::str_extract(episode_id, "-[0-9]+-") %>% stringr::str_remove_all("-")))
  } else {
    return(episode_id)
  }
}

data_dirty_2021 <-
  data_raw_2021 %>%
  dplyr::rename(
    dataobservacio = dataobservacio,
    geometry = areaafectada,
    new_episode = nouoantic,
    affected_trees_type = arbresnousafectats,
    affected_trees_distribution = distribucio,
    species_id = nomespecie,
    cover_perc = recobriment,
    affected_trees_perc = arbres_afectats_perc,
    mortality_perc = mortalitat_perc,
    defoliation_perc = defoliacio_perc,
    decoloration_perc = decoloracio_perc
  ) %>%
  # get the geometry in the correct format, calculate episode area and tranform year to integer
  dplyr::mutate(
    geometry = sf::st_as_sfc(lapply(.$geometry, sf:::hex_to_raw), EWKB = TRUE),
    episode_area = as.numeric(sf::st_area(geometry)/10000),
    year = vctrs::vec_cast(year, integer()),
    episode_id = purrr::map_chr(episode_id, episode_id_10_county_fix)
  ) %>%
  # reorganizing variables
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area,
    dplyr::everything(), -tipusafectacio, -year_id, -dataobservacio
  )

```

## 2022 data (update March 2023)

We need to create the 2022 raw data and perform the cleaning process

```{r data_raw_2022}
data_raw_2022 <-
  readr::read_csv2('dbc22.csv') %>%
  # convert to numeric
  dplyr::mutate(
    dplyr::across(.cols = c(recobriment, dplyr::ends_with('perc')), .fns = as.numeric)
  ) %>%
  # separate episode id from the year
  tidyr::separate(
    col = codi, into = c("episode_id", "year_id"), sep = 6
  ) %>%
  # fix episode code in worng ones
  dplyr::mutate(
    episode_id = dplyr::case_when(
      episode_id == "10-13-" ~ "10-013",
      episode_id == "10-14-" ~ "10-014",
      episode_id == "10-15-" ~ "10-015",
      episode_id == "10-16-" ~ "10-016",
      episode_id == "10-17-" ~ "10-017",
      episode_id == "10-19-" ~ "10-019",
      episode_id == "41-24-" ~ "41-024",
      # episodes 00-* this year corresponds to 02-*
      episode_id == "00-037" ~ "02-037",
      episode_id == "00-038" ~ "02-038",
      TRUE ~ episode_id
    )
  ) %>% 
  # remove especial year codes and convert to numeric with full year number
  # obtain the year from the sampling date and use it
  dplyr::mutate(
    year_id = stringr::str_remove_all(year_id, '[-abcde]'),
    year_id = as.numeric(year_id) + 2000,
    year = lubridate::year(dataobservacio)
  )

year_mismatch <- data_raw_2022 %>%
  filter(year_id != year) %>%
  select(episode_id, year_id, year, dataobservacio)
```

Now we have the raw data, is time to create the dirty one.

```{r data_dirty_2022}
data_dirty_2022 <-
  data_raw_2022 %>%
  dplyr::rename(
    dataobservacio = dataobservacio,
    geometry = areaafectada,
    new_episode = nouoantic,
    affected_trees_type = arbresnousafectats,
    affected_trees_distribution = distribucio,
    species_id = nomespecie,
    cover_perc = recobriment,
    affected_trees_perc = arbres_afectats_perc,
    mortality_perc = mortalitat_perc,
    defoliation_perc = defoliacio_perc,
    decoloration_perc = decoloracio_perc
  ) %>%
  # get the geometry in the correct format, calculate episode area and tranform year to integer
  dplyr::mutate(
    geometry = sf::st_as_sfc(lapply(.$geometry, sf:::hex_to_raw), EWKB = TRUE),
    episode_area = as.numeric(sf::st_area(geometry)/10000),
    year = vctrs::vec_cast(year, integer())
  ) %>%
  # reorganizing variables
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area,
    dplyr::everything(), -tipusafectacio, -year_id, -dataobservacio
  )

```

# 2012 data

With the 2011 list, we select the episodes that already exist and format them:

```{r data_old_2012}
data_raw_2012 <- data_raw_2012_2013 %>%
  dplyr::filter(year == 2012)
data_raw_2013 <- data_raw_2012_2013 %>%
  dplyr::filter(year == 2013)

data_old_2012 <-
  data_raw_2012 %>%
  dplyr::filter(episode_id %in% episodes_existing_in_2011) %>%
  dplyr::mutate(
    mortality_perc = NA,
    defoliation_perc = NA,
    decoloration_perc = NA,
    new_episode = FALSE,
    episode_area = as.numeric(sf::st_area(geometry))/10000
  ) %>%
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area, new_episode,
    affected_trees_distribution, cover_perc, affected_trees_perc, mortality_perc,
    defoliation_perc, decoloration_perc
  )
```

And now we get the new episodes that fulfill the requirements explained above:

```{r data_new_2012}
episodes_started_in_2012 <-
  data_raw_2012 %>%
  dplyr::filter(!episode_id %in% episodes_existing_in_2011) %>%
  dplyr::mutate(
    mortalitat = dplyr::if_else(mortalitat == 'S', TRUE, FALSE),
    defoliacio = dplyr::if_else(defoliacio == 'S', TRUE, FALSE),
    decoloracio = dplyr::if_else(decoloracio == 'S', TRUE, FALSE)
  ) %>%
  dplyr::filter(
    (mortalitat & affected_trees_perc >= 5) |
      (any(defoliacio, decoloracio) & affected_trees_perc >= 50)
  ) %>%
  dplyr::pull(episode_id) %>%
  unique()

data_new_2012 <-
  data_raw_2012 %>%
  dplyr::filter(episode_id %in% episodes_started_in_2012) %>%
  dplyr::mutate(
    mortality_perc = NA,
    defoliation_perc = NA,
    decoloration_perc = NA,
    new_episode = TRUE,
    episode_area = as.numeric(sf::st_area(geometry))/10000
  ) %>%
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area, new_episode,
    affected_trees_distribution, cover_perc, affected_trees_perc, mortality_perc,
    defoliation_perc, decoloration_perc
  )
```

And now, we can join them to get the 2012 dirty data

```{r data_dirty_2012}
data_dirty_2012 <-
  dplyr::bind_rows(data_new_2012, data_old_2012) %>%
  # distinct will remove any duplicated entries
  dplyr::distinct() %>%
  dplyr::arrange(episode_id, year)

data_dirty_2012
```

## 2012 data checks

Now that we have the old and new episodes for 2012 we are gonna perform some
checks:

1. Species checks
  - We check if there are duplicated species on the episode
  - We check if there are new species in the episode (Not for 2012, as we dont have
    species in 2011 data)

2. Polygons checks
  - We check if all the species polygons in the episode intersect
  - We check the max distance between the species polygons in the episode
  - We check if the species polygons in the episode intersect with previous
    years of the same episode.

```{r checks_2012}
data_dirty_2012_checks <- data_dirty_2012 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_raw_2011) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_raw_2011) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()
```

We can check the different combinations of checks present in the 2012 data:

```{r checks_2012_comb}
summary_checks_2012 <- data_dirty_2012_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2012
```

### Custom cleaning

Now we have an idea of the episodes problems. There is no automatic way of fixing duplicated species or
new/errors, so we go group by group trying to fix it.

```{r data_2012_problems}
data_dirty_2012_ok <- data_dirty_2012_checks %>%
  dplyr::filter(check_meaning == 'Ok')

data_dirty_2012_duplicated_species <- data_dirty_2012_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2012_duplicated_species_wrong_poly <- data_dirty_2012_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species in wrong poly (unknown)')

data_dirty_2012_error <- data_dirty_2012_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```


#### Duplicated species

We can see that five episodes have duplicated species with no explanation
whatsoever. As we said before, we don't have enough data to automatically trying
to fix them, so we do it manually for each one:

  - "14-023": In this case I trust the `cover_perc` variable. The bigger polygon
  has more "reasonable" values for cover, so I choose that one.
  - "15-004": Four different *Pinus uncinata* registries. `cover_perc` and
  `affected_trees_perc` is really similar, and `episode_area` also. So I choose
  pseudo-randomly (max area).
  - "19-018": very similar area, same cover, but affectation is very low in one
  and very high in another. I choose the high one, as the episode is new.
  - ~~"32-001": very similar area, and the raw data says it has decoloration, so we take
  the 70 percent decoloration value.~~ REMOVED
  - "40-005": Similar values, but one polygon has 270 ha and the other 4ha. I
  trust the smaller one, as an episode with 270 ha maybe is too big

```{r duplicated_species_fixes}
data_dirty_2012_duplicated_species_fixed <-
  data_dirty_2012_duplicated_species %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name == "14-023") {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      if (episode_name == "15-004") {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      if (episode_name == "19-018") {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      # if (episode_name == "32-001") {
      #   res <- episode_data %>%
      #     dplyr::filter(affected_trees_perc == max(affected_trees_perc))
      # }
      if (episode_name == "40-005") {
        res <- episode_data %>%
          dplyr::filter(episode_area == min(episode_area))
      }
      return(res)
    }
  )
```

#### Duplicated species in the wrong poly (unknown)

We have two duplicated species episodes that have completely different polygons for each of the dupes:

  - "02-009":_Is a new episode, so we don't have past information, and we have two different polygons.
  Looking to the future data, we can see that the smaller one is the one that continues in the time with this
  code, so we select that one
  
  - "24-039": Again, is a new episode, with different polygons. Looking at the future data indicates that the
  bigger polygon is the one that continues in time.

```{r duplicated_species_fixes_2}
data_dirty_2012_duplicated_species_wrong_poly_fixed <-
  data_dirty_2012_duplicated_species_wrong_poly %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name == "02-009") {
        res <- episode_data %>%
          dplyr::filter(episode_area == min(episode_area))
      }
      if (episode_name == "24-039") {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      return(res)
    }
  )
```


#### New episodes or errors

Here we have 3 episodes that are errors or new episodes with old codes. I don't know really, I just now that
these episodes polygons don't intersect with old polygons:

  - "14-010": Only one species, the polygon don't intersect with old polygons, and the distance between old
  and new polygons is like 1.2 km. The polygon in 2012 intersects with future polygons, so I tend to believe
  this site, no fix needed.
  
  - "38-001": Duplicated species in different polygons, but they intersect. Also, distance with old polygons is
  like 5.6 km. This episode dissapear in the future (no data in 2014-2020 period). So I tend to eliminate this
  one.
  
  - "38-002": Only one species, the polygon don't intersect with old polygons, and the distance with the old
  is bigger than 37 km. But in this case future episodes intersect with the 2012 polygon, so I maintain it,
  no fix needed.
```{r}
create_polygon_plot('14-010', data_raw_2011, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2012))
create_polygon_plot('38-001', data_raw_2011, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2012))
create_polygon_plot('38-002', data_raw_2011, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2012))
```
  

```{r new_or_error_fixes}
data_dirty_2012_error_fixed <- data_dirty_2012_error %>%
  dplyr::filter(episode_id != "38-001")
```


## Clean data for 2012

Finally we have the clean data for 2012:

```{r data_clean_2012}
data_clean_2012 <- list(
  data_dirty_2012_ok, data_dirty_2012_error_fixed, data_dirty_2012_duplicated_species_fixed,
  data_dirty_2012_duplicated_species_wrong_poly_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

# 2013 data

Now we can repeat the process for the 2013 data, using now 2012 as starting point:

```{r data_2013_process}
episodes_existing_in_2012 <- data_clean_2012 %>% pull(episode_id) %>% unique()

data_old_2013 <-
  data_raw_2013 %>%
  dplyr::filter(episode_id %in% episodes_existing_in_2012) %>%
  dplyr::mutate(
    mortality_perc = NA,
    defoliation_perc = NA,
    decoloration_perc = NA,
    new_episode = FALSE,
    episode_area = as.numeric(sf::st_area(geometry))/10000
  ) %>%
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area, new_episode,
    affected_trees_distribution, cover_perc, affected_trees_perc, mortality_perc,
    defoliation_perc, decoloration_perc
  )

episodes_started_in_2013 <-
  data_raw_2013 %>%
  dplyr::filter(!episode_id %in% episodes_existing_in_2012) %>%
  dplyr::mutate(
    mortalitat = dplyr::if_else(mortalitat == 'S', TRUE, FALSE),
    defoliacio = dplyr::if_else(defoliacio == 'S', TRUE, FALSE),
    decoloracio = dplyr::if_else(decoloracio == 'S', TRUE, FALSE)
  ) %>%
  dplyr::filter(
    (mortalitat & affected_trees_perc >= 5) |
      (any(defoliacio, decoloracio) & affected_trees_perc >= 50)
  ) %>%
  dplyr::pull(episode_id) %>%
  unique()

data_new_2013 <-
  data_raw_2013 %>%
  dplyr::filter(episode_id %in% episodes_started_in_2013) %>%
  dplyr::mutate(
    mortality_perc = NA,
    defoliation_perc = NA,
    decoloration_perc = NA,
    new_episode = TRUE,
    episode_area = as.numeric(sf::st_area(geometry))/10000
  ) %>%
  dplyr::select(
    episode_id, year, species_id, geometry, episode_area, new_episode,
    affected_trees_distribution, cover_perc, affected_trees_perc, mortality_perc,
    defoliation_perc, decoloration_perc
  )

data_dirty_2013 <-
  dplyr::bind_rows(data_new_2013, data_old_2013) %>%
  # distinct will remove any duplicated entries
  dplyr::distinct() %>%
  dplyr::arrange(episode_id, year)

data_dirty_2013
```

Now we have the dirty data for 2013. Also, we have a list of new episodes that have been not included in 2013
because they don't fulfill the requirements to be included:

```{r not_included episodes}
data_not_included_2013 <- data_raw_2013 %>% anti_join(data_dirty_2013)
data_not_included_2013
```

This episodes will be not considered.

## 2013 data checks

```{r checks_2013}
data_dirty_2013_checks <- data_dirty_2013 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_clean_2012) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_clean_2012) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2013 <- data_dirty_2013_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2013
```

### Custom cleaning

Now we have an idea of the episodes problems. There is no automatic way of fixing duplicated species or
new/errors, so we go group by group trying to fix it.

```{r data_2013_problems}
data_dirty_2013_ok <- data_dirty_2013_checks %>%
  dplyr::filter(check_meaning == 'Ok')

data_dirty_2013_duplicated_species <- data_dirty_2013_checks %>%
  dplyr::filter(check_meaning == 'New species others / Duplicated species')

data_dirty_2013_new_species_populus <- data_dirty_2013_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2013_new_species_others <- data_dirty_2013_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2013_error <- data_dirty_2013_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### Duplicated species

We have one episode with duplicated species this year, but it also coincides with a new
species in this site. As we said before, we don't have enough data to automatically trying
to fix them, so we do it manually for each one:

  - "02-003": The new species is *Pinus halepensis* that is also the one duplicated. The only
  difference is the cover perc for that species. I checked the future data and it seems that
  the 20 cover value makes more sense

```{r duplicated_species_fixes_2013}
data_dirty_2013_duplicated_species_fixed <-
  data_dirty_2013_duplicated_species %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name == "02-003") {
        res <- episode_data %>%
          dplyr::filter(cover_perc != min(cover_perc))
      }
      return(res)
    }
  )
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 3 episodes with this species as new:

  - "06-001" and "16-009" are mistakes, it should be *Pinus nigra*
  - "19-001" Does not seem a mistake, future data also shows *Populus nigra* and previous data don't
  have any *Pinus nigra*

```{r new_species_populus_2013}
data_dirty_2013_new_species_populus_fixed <-
  data_dirty_2013_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("06-001", "16-009")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```


#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok

```{r new_species_others_fix}
data_dirty_2013_new_species_others_fixed <-
  data_dirty_2013_new_species_others
```

#### New episodes or errors

We see that we have 9 episodes that can be new episodes with wrong code (reusing the code). 7 of them
have new species and 2 don't. All episodes dont intersect with their previous polygons and they are more
than 1km away from the previous polygons:

+ Code reuse cases:

  - "20-012": Polygon dont intersects with 2012 polygon they are at 6.5 km, but intersects with future
  (2015:2017) data. This means that this is a reuse of the code.
  - "40-003": Like "20-012", separated for more than 25km, this seems to be a case of code reuse
  - "31-001": A classic case of code reusing. 2011-2012 share polygons, 2013-2014 share polygons (20km away),
  and 2016-2020 share polygons.
  - "31-002": Exactly same case as before
  - "31-007": Exactly the same as before, but no 2011 data.
  - "31-008": Exactly the same as before, but no 2011 data. "31" is gonna be a funny county :(

Code reuse is fixed in the following manner. Newest episode maintains the code, but previous episodes dont
related (2012 in this case) get their codes modified adding the year the episode finished: i.e. "40-003" in
2013 maintains the code, this way it will be able to join with the future data, but 2012 episode gets
recoded to "40-003-2012"

```{r}
create_polygon_plot('20-012', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('40-003', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('31-001', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('31-002', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('31-007', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('31-008', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
```


+ No fixes cases:  
  - "24-043": Same as before, but they are separate by ~ 3km. Even with that, I tend to believe is the same
  episode, so no fix needed.

```{r}
create_polygon_plot('06-027', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('06-045', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('24-043', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
```

+ What the fuck cases:
  - "32-013": Like the previous one. "32" is gonna be a funny county :(
  - "32-008": Amazing case. 2013 doesn't intersect with 2012, but neither with 2014 or following years. BUT,
  2014 doesn't intersect with 2015 either. The only usable years for this site is 2017 to 2019.
  
```{r}
create_polygon_plot('32-008', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
create_polygon_plot('32-013', data_dirty_2013, data_dirty_2012, data_dirty_2014_2020 %>% filter(year > 2013))
```
  

What the fuck cases are removed, if we find a way to understand them we will fix them.

```{r error_or_new_2013_fix}
# remove what the fuck cases
data_dirty_2013_error_fixed <-
  data_dirty_2013_error %>%
  dplyr::filter(
    !episode_id %in% c("32-013", "32-008")
  )
  
# update clean data from previous years
data_clean_2012 <- data_clean_2012 %>%
  dplyr::mutate(
    original_episode_id = episode_id,
    episode_id = dplyr::if_else(
      episode_id %in% c("20-012", "40-003", "31-001", "31-002", "31-007", "31-008"),
      glue::glue("{episode_id}-2012"),
      episode_id
    ),
    new_episode = dplyr::if_else(
      episode_id %in% c("20-012", "40-003", "31-001", "31-002", "31-007", "31-008"),
      TRUE,
      new_episode
    )
  )
```


## Clean data for 2013

Finally we have the clean data for 2013:

```{r data_clean_2013}
data_clean_2013 <- list(
  data_dirty_2013_ok, data_dirty_2013_duplicated_species_fixed,
  data_dirty_2013_new_species_populus_fixed, data_dirty_2013_new_species_others_fixed,
  data_dirty_2013_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```


## Deboscat data

Now that we have 2012 and 2013, we have the base data to start working. As with
following years we need to probably update codes (reusing) and other stuff, and
include the year data as it is cleaned, let's create the final table where we store
the cleaned data for each year:

```{r dbc_data_ation}
data_dirty_deboscat <- data_clean_2012 %>%
  dplyr::bind_rows(data_clean_2013)
data_dirty_deboscat
```

# 2014 data

We repeat the process for 2014 data:

```{r data_2014_process}
data_dirty_2014 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2014) %>%
  dplyr::distinct() %>%
  {
    data_raw_2014 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2014 data checks

```{r data_2014_checks}
data_dirty_2014_checks <- data_dirty_2014 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2014 <- data_dirty_2014_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2014
```


### Custom cleaning

Now we have an idea about how the 2014 episodes behave. Let's make the round of custom cleanings:

```{r data_2014_problems}
data_dirty_2014_ok <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2014_duplicated_species <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2014_duplicated_species_wrong_poly <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species in wrong poly (known)')

data_dirty_2014_new_species_populus <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2014_new_species_others <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2014_error <- data_dirty_2014_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```


#### Duplicated species

We have 2 episodes with duplicated species:

  - "24-071": Here, *Q. humilis* is duplicated, the only difference is the `cover_perc`. Looking on the
  future data seems like a cover of 30% is the correct
  - "35-025": Here, all species are duplicated in slightly different polygons, but with same values, except
  for *Quercus ilex*, that only appears in one set. Looking the future data seems like *Q. ilex* exists, so
  I choose the duped set that contains *Q. ilex* (bigger area).

We also have a episode ("25-035") with duplicated species in the wrong poly. But we know which polygon is
wrong, so the fix is easy.

```{r duplicated_species_fix_2014}
data_dirty_2014_duplicated_species_fixed <-
  data_dirty_2014_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '24-071') {
        res <- episode_data %>%
          dplyr::filter(!(species_id == 'Quercus humilis' & cover_perc == 30))
      }
      if (episode_name == '35-025') {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      return(res)
    }
  )

data_dirty_2014_duplicated_species_wrong_poly_fixed <-
  data_dirty_2014_duplicated_species_wrong_poly %>%
  dplyr::filter(!check_old_polygon_intersects_ind)
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 7 episodes with this species as new:

  - "04-020", "25-001" and "35-004" are mistakes, it should be *Pinus nigra*
  - "04-034", "14-051", "14-054", and "14-055" do not seem mistakes

```{r new_species_populus_2014}
data_dirty_2014_new_species_populus_fixed <-
  data_dirty_2014_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("04-020", "25-001", "35-004")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok, except for

  - Amazing case: "14-026" and "14-062" has interchanged codes, we need to fix this
  
```{r amazing_case_14-026_14-062, echo=FALSE}
create_polygon_plot('14-026', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
create_polygon_plot('14-062', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
```
  

```{r new_species_others_fix_2014}
data_dirty_2014_new_species_others_fixed <-
  data_dirty_2014_new_species_others %>%
  dplyr::mutate(
    episode_id = dplyr::case_when(
      episode_id == '14-026' ~ glue::glue('14-062'),
      episode_id == '14-062' ~ glue::glue('14-026'),
      TRUE ~ episode_id
    )
  )
```

#### New episodes or errors

We see that we have 4 episodes that can be new episodes with wrong code (reusing the code). All episodes dont
intersect with their previous polygons and they are more than 1km away from the previous polygons:

+ No fixes cases:  
  - "16-002": In this case, 2014 doesn't intersect with 2012 and 2013, but distance from 2012 and following
  years is slightly bigger than 1000m (~ 1160m), so I'm gonna assume that is the same episode all years, so no
  fix needed.
  
```{r}
create_polygon_plot('16-002', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
```


+ What the fuck cases:
  - "32-007": What the fuck! 30 km distance. But also 2013 to 2018 are mixed 2013 and 2015 intersects, but
  not with 2014,2016,2017 and 2018, that intersect among them.
  - "32-013": Like the previous one. "32" is gonna be a funny county :(
  - "32-008": Amazing case. 2013 doesn't intersect with 2012, but neither with 2014 or following years. BUT,
  2014 doesn't intersect with 2015 either. The only usable years for this site is 2017 to 2019.

```{r}
create_polygon_plot('32-007', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
create_polygon_plot('32-013', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
create_polygon_plot('32-008', data_dirty_2014, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2014))
```

```{r error_or_new_2014_fix}
# remove what the fuck cases
data_dirty_2014_error_fixed <-
  data_dirty_2014_error %>%
  dplyr::filter(
    !episode_id %in% c("32-007", "32-013", "32-008")
  )
```

## Clean data for 2014

Finally we have the clean data for 2014:

```{r data_clean_2014}
data_clean_2014 <- list(
  data_dirty_2014_ok, data_dirty_2014_duplicated_species_fixed, data_dirty_2014_duplicated_species_wrong_poly_fixed,
  data_dirty_2014_new_species_populus_fixed, data_dirty_2014_new_species_others_fixed,
  data_dirty_2014_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2014 clean data.

```{r deboscat_update_2014}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2014) %>%
  dplyr::arrange(episode_id, year)
```


# 2015 data

We repeat the process for 2015 data:

```{r data_2015_process}
data_dirty_2015 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2015) %>%
  dplyr::distinct() %>%
  {
    data_raw_2015 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2015 data checks

```{r data_2015_checks}
data_dirty_2015_checks <- data_dirty_2015 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2015 <- data_dirty_2015_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2015
```

### Custom cleaning

Now we have an idea about how the 2015 episodes behave. Let's make the round of custom cleanings:

```{r data_2015_problems}
data_dirty_2015_ok <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2015_duplicated_species <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2015_duplicated_new_species <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning == 'New species others / Duplicated species')

data_dirty_2015_new_species_populus <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2015_new_species_others <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2015_error <- data_dirty_2015_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```


#### Duplicated species

We have 1 episode with duplicated species:

  - "04-010": Here, *P. sylvestrys* is duplicated. The only difference is the polygon, and differences are
  minimal. I choose the bigger one.

We also have a episode ("26-034") with duplicated species and new species. THe duplicated species is a
*Q. humilis* that in reality is a *Q. ilex*, present in past and future data. We know which one by the cover,
being *Q. ilex* the smaller one.

```{r duplicated_species_fix_2015}
data_dirty_2015_duplicated_species_fixed <-
  data_dirty_2015_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '04-010') {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      return(res)
    }
  )

data_dirty_2015_duplicated_new_species_fixed <-
  data_dirty_2015_duplicated_new_species %>%
  dplyr::mutate(
    species_id = dplyr::if_else(species_id == 'Quercus humilis' & cover_perc == 10, 'Quercus ilex', species_id)
  )
```


#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 1 episode with this species as new:

  - "04-015" is a mistake, it should be *Pinus nigra*

```{r new_species_populus_2015}
data_dirty_2015_new_species_populus_fixed <-
  data_dirty_2015_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("04-015")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2015}
data_dirty_2015_new_species_others_fixed <-
  data_dirty_2015_new_species_others
```

#### New episodes or errors

We see that we have 5 episodes that can be new episodes with wrong code (reusing the code). All episodes dont
intersect with their previous polygons and they are more than 1km away from the previous polygons:

+ What the fuck cases:
  - "32-007": What the fuck! 30 km distance. But also 2013 to 2018 are mixed 2013 and 2015 intersects, but
  not with 2014,2016,2017 and 2018, that intersect among them.
  - "32-008": Amazing case. 2013 doesn't intersect with 2012, but neither with 2014 or following years. BUT,
  2014 doesn't intersect with 2015 either. The only usable years for this site is 2017 to 2019.
  - ~~"32-004" to "32-006", no idea, but in all these the 2015 seems different from the rest and dont continue
  in time~~ REMOVED

```{r}
# create_polygon_plot('32-004', data_dirty_2015, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2015))
# create_polygon_plot('32-005', data_dirty_2015, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2015))
# create_polygon_plot('32-006', data_dirty_2015, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2015))
create_polygon_plot('32-007', data_dirty_2015, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2015))
create_polygon_plot('32-008', data_dirty_2015, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2015))
```

```{r error_or_new_2015_fix}
# remove what the fuck cases
data_dirty_2015_error_fixed <-
  data_dirty_2015_error %>%
  dplyr::filter(
    !episode_id %in% c("32-007", "32-008")
  )
```

## Clean data for 2015

Finally we have the clean data for 2015:

```{r data_clean_2015}
data_clean_2015 <- list(
  data_dirty_2015_ok, data_dirty_2015_duplicated_species_fixed, data_dirty_2015_duplicated_new_species_fixed,
  data_dirty_2015_new_species_populus_fixed, data_dirty_2015_new_species_others_fixed,
  data_dirty_2015_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2015 clean data.

```{r deboscat_update_2015}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2015) %>%
  dplyr::arrange(episode_id, year)
```

# 2016 data

We repeat the process for 2016 data:

```{r data_2016_process}
data_dirty_2016 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2016) %>%
  dplyr::distinct() %>%
  {
    data_raw_2016 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2016 data checks

```{r data_2016_checks}
data_dirty_2016_checks <- data_dirty_2016 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2016 <- data_dirty_2016_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2016
```

### Custom cleaning

Now we have an idea about how the 2016 episodes behave. Let's make the round of custom cleanings:

```{r data_2016_problems}
data_dirty_2016_ok <- data_dirty_2016_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2016_duplicated_species <- data_dirty_2016_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2016_new_species_populus <- data_dirty_2016_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2016_new_species_others <- data_dirty_2016_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2016_error <- data_dirty_2016_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### Duplicated species

We have 4 episodes with duplicated species:

  - "02-019": 2 *Acer campestre* when one should be *Acer monspesulanum*
  - "07-016": 2 repeated *Quercus ilex* all with zero values. THe difference is in the cover, so I choose the
  one closest to the mean of the other years
  - "23-012": 2 sets of species with same values and slightly different polygon area. I choose the bigger
  - "24-084": 2 repeated *Quercus ilex*. It makes sense to choose the one with more affected trees, as it
  follows the trend.

```{r duplicated_species_fix_2016}
data_dirty_2016_duplicated_species_fixed <-
  data_dirty_2016_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '02-019') {
        res <- episode_data %>%
          dplyr::mutate(
            species_id = dplyr::if_else(
              species_id == 'Acer campestre' & cover_perc == 10, 'Acer monspessulanum', species_id
            )
          )
      }
      if (episode_name == '07-016') {
        res <- episode_data %>%
          dplyr::filter(!(species_id == 'Quercus ilex' & cover_perc == 5))
      }
      if (episode_name == '23-012') {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      if (episode_name == '24-084') {
        res <- episode_data %>%
          dplyr::filter(!(species_id == 'Quercus ilex' & affected_trees_perc == 10))
      }
      return(res)
    }
  )
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 3 episodes with this species as new:

  - "04-012", "26-032" and "35-004" are all mistakes, they should be *Pinus nigra*

```{r new_species_populus_2016}
data_dirty_2016_new_species_populus_fixed <-
  data_dirty_2016_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("04-012", "26-032", "35-004")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2016}
data_dirty_2016_new_species_others_fixed <-
  data_dirty_2016_new_species_others
```

#### New episodes or errors

We see that we have 10 episodes that can be new episodes with wrong code (reusing the code). All episodes
don't intersect with old polygons and 8 of them have new species:

+ Code reuse cases:

  - "02-010": Polygon does not intersect with 2012 polygon (no 2013, 2014 or 2015), and they are separated by
  more than 140 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - ~~"06-048": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 12 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.~~ REMOVED
  - "24-073": Polygon does not intersect with 2013 polygon (no 2014 or 2015), and they are separated by
  more than 18 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - "31-001": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 5 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - "31-002": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 4 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - "31-004": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 13 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - "31-006": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 17 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - "31-007": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 16 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  - ~~"32-007": **Finally!!**, we can start using this episode. Code reusing here, so I will change the code in
  the old episodes.~~ REMOVED
  - "32-012": Polygon does not intersect with 2014 polygon (no 2015), and they are separated by
  more than 6 km, but intersects with future polygons. Code reusing here, so I will change the code in the
  old episodes.
  
  All this episodes are setted as new episodes, but they only stay in the database if they fulfill the
  expectations for new episodes (mortality, affectation and area thresholds)
  

Also, even if not detected (distance less than 1000), 31-005 must be changed:

```{r}
create_polygon_plot('31-005', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
```
  
  
  
```{r code_reuse_plots_2016}
create_polygon_plot('02-010', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
# create_polygon_plot('06-048', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('24-073', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('31-001', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('31-002', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('31-004', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('31-006', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('31-007', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
# create_polygon_plot('32-007', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('32-012', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
```
  

+ What the fuck cases:
  - ~~"32-002": Polygon doesn't intersect with 2015 polygon, and they are sepearated by more than 6 km. Im not
  sure there is intersection with future polygons because it dissapears until 2020.~~ REMOVED
  - "32-009": 2016 polygon seems an isolated polygon. Not sure, so not included. Future polygons will intersect
  - "32-013": Crazyness, this episode is forbidden to appear ever in the final database.
  
```{r wtf_plots_2016}
# create_polygon_plot('32-002', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('32-009', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
create_polygon_plot('32-013', data_dirty_2016, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2016))
```

```{r error_or_new_2016_fix}
# remove what the fuck cases
data_dirty_2016_error_fixed <-
  data_dirty_2016_error %>%
  dplyr::filter(
    !episode_id %in% c("32-013", "32-009")
  ) %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        '02-010', '24-073', '31-001', '31-002',
        '31-004', '31-006', '31-007', '32-012'
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  }

data_dirty_2016_ok_fixed <-
  data_dirty_2016_ok %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        '31-005'
      ),
      TRUE,
      new_episode
    )
  )
  

# update clean data from pervious years
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::mutate(
    original_episode_id = episode_id,
    episode_id = dplyr::if_else(
      episode_id %in% c(
        '02-010', '24-073', '31-001', '31-002',
        '31-004', '31-005', '31-006', '31-007', '32-012'
      ),
      glue::glue("{episode_id}-2015"),
      episode_id
    )
  )
```

## Clean data for 2016

Finally we have the clean data for 2016:

```{r data_clean_2016}
data_clean_2016 <- list(
  data_dirty_2016_ok_fixed, data_dirty_2016_duplicated_species_fixed,
  data_dirty_2016_new_species_populus_fixed, data_dirty_2016_new_species_others_fixed,
  data_dirty_2016_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2016 clean data.

```{r deboscat_update_2016}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2016) %>%
  dplyr::arrange(episode_id, year)
```

# 2017 data

We repeat the process for 2017 data:

```{r data_2017_process}
data_dirty_2017 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2017) %>%
  dplyr::distinct() %>%
  {
    data_raw_2017 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2017 data checks

```{r data_2017_checks}
data_dirty_2017_checks <- data_dirty_2017 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2017 <- data_dirty_2017_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2017
```

### Custom cleaning

Now we have an idea about how the 2017 episodes behave. Let's make the round of custom cleanings:

```{r data_2017_problems}
data_dirty_2017_ok <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2017_duplicated_species <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2017_duplicated_species_wrong_poly <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species in wrong poly (known)')

data_dirty_2017_new_species_populus <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2017_new_species_others <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2017_error <- data_dirty_2017_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### Duplicated species

We have 1 episodes with duplicated species:

  - "27-001": 2 sets of species. Both sets have slightly different areas and different values for
  `affected_trees_perc` for *Pinus halepensis*. This episode is new but dissapear in the future, so I choose
  randomly

We also have a episode ("06-048") with duplicated species in the wrong poly. But we know which polygon is
wrong, so the fix is easy.

```{r duplicated_species_fix_2017}
data_dirty_2017_duplicated_species_fixed <-
  data_dirty_2017_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '27-001') {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      return(res)
    }
  )

data_dirty_2017_duplicated_species_wrong_poly_fixed <-
  data_dirty_2017_duplicated_species_wrong_poly %>%
  dplyr::filter(!check_old_polygon_intersects_ind)
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 3 episodes with this species as new:

  - "35-025" is a mistake, it should be *Pinus nigra*
  - "07-018" and "24-034" all seem correct

```{r new_species_populus_2017}
data_dirty_2017_new_species_populus_fixed <-
  data_dirty_2017_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("35-025")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2017}
data_dirty_2017_new_species_others_fixed <-
  data_dirty_2017_new_species_others
```

#### New episodes or errors

We see that we have 8 episodes that can be new episodes with wrong code (reusing the code). All episodes
don't intersect with old polygons and 7 of them have new species:

+ Code reuse cases:
  
  - "18-001": All species are new, the episode ended in 2014. Code reusing here, so I will change the code in
  the old episodes.
  - "25-037": Almost 13 km of difference, new species and future data intersects with this year.
  Code reusing here, so I will change the code in the old episodes.
  - "31-008": Almost 21 km of difference, new species and future data intersects with this year.
  Code reusing here, so I will change the code in the old episodes.
  - "31-009": Almost 7 km of difference, new species and future data intersects with this year.
  Code reusing here, so I will change the code in the old episodes.
  - ~~"32-001": **Finally**, it intersects with the future ones.~~ REMOVED
  - ~~"32-004": **Finally**, it intersects with the future ones.~~ REMOVED
  - "32-008": **Finally**, it intersects with the future ones, **BUT** it does not fulfill requirements
  - "32-009": **Finally**, it intersects with the future ones.
  - "32-013": **Finally**, it intersects with the future ones, **BUT** it does not fulfill requirements
  
  All this episodes are setted as new episodes, but they only stay in the database if they fulfill the
  expectations for new episodes (mortality, affectation and area thresholds)


Also, even if not detected (distance less than 1000), 06-046 must be changed:

```{r}
create_polygon_plot('06-046', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
```

  
```{r code_reuse_plots_2017}
create_polygon_plot('18-001', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('25-037', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('31-008', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('31-009', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
# create_polygon_plot('32-001', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
# create_polygon_plot('32-004', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('32-008', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('32-009', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
create_polygon_plot('32-013', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
```
  

+ No fix cases:

  - "04-036": There is only 2 km difference, no new species and no future cases, and data seems consistent.
  
  
```{r no_fix_plots_2017}
create_polygon_plot('04-036', data_dirty_2017, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2017))
```
  

```{r error_or_new_2017_fix}
data_dirty_2017_error_fixed <-
  data_dirty_2017_error %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        '18-001', '25-037', '31-008', '31-009',
        '32-008', '32-009', '32-013'
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  }

# change also 06-046 as it is in other group
data_dirty_2017_ok_fixed <-
  data_dirty_2017_ok %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        '06-046'
      ),
      TRUE,
      new_episode
    )
  )
  

# update clean data from pervious years
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::mutate(
    original_episode_id = episode_id,
    episode_id = dplyr::if_else(
      episode_id %in% c(
        '06-046','18-001', '25-037', '31-008', '31-009',
        '32-008', '32-009', '32-013'
      ),
      glue::glue("{episode_id}-2016"),
      episode_id
    )
  )
```

## Clean data for 2017

Finally we have the clean data for 2017:

```{r data_clean_2017}
data_clean_2017 <- list(
  data_dirty_2017_ok_fixed, data_dirty_2017_duplicated_species_fixed, data_dirty_2017_duplicated_species_wrong_poly_fixed,
  data_dirty_2017_new_species_populus_fixed, data_dirty_2017_new_species_others_fixed,
  data_dirty_2017_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2017 clean data.

```{r deboscat_update_2017}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2017) %>%
  dplyr::arrange(episode_id, year)
```

# 2018 data

We repeat the process for 2018 data, but:

```{r data_2018_process}
data_dirty_2018 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2018) %>%
  dplyr::distinct() %>%
  {
    data_raw_2018 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```


## 2018 data checks

```{r data_2018_checks}
data_dirty_2018_checks <- data_dirty_2018 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2018 <- data_dirty_2018_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2018
```

### Custom cleaning

Now we have an idea about how the 2018 episodes behave. Let's make the round of custom cleanings:

```{r data_2018_problems}
data_dirty_2018_ok <- data_dirty_2018_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2018_duplicated_species <- data_dirty_2018_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2018_new_species_populus <- data_dirty_2018_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2018_new_species_others <- data_dirty_2018_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2018_error <- data_dirty_2018_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### Duplicated species

We have 1 episodes with duplicated species:

  - "15-002": 2 *P. uncinata* when one should be *Abies alba*. We rename the one with 10% of cover as it seems
  to be in concordance with the other years data

```{r duplicated_species_fix_2018}
data_dirty_2018_duplicated_species_fixed <-
  data_dirty_2018_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '15-002') {
        res <- episode_data %>%
          dplyr::mutate(
            species_id = dplyr::if_else(
              species_id == 'Pinus uncinata' & cover_perc == 10, 'Abies alba', species_id
            )
          )
      }
      return(res)
    }
  )
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 3 episodes with this species as new:

  - "04-033", "32-012" and "35-009" are all mistakes, they should be *Pinus nigra*

```{r new_species_populus_2018}
data_dirty_2018_new_species_populus_fixed <-
  data_dirty_2018_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("04-033", "32-012", "35-009")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2018}
data_dirty_2018_new_species_others_fixed <-
  data_dirty_2018_new_species_others
```

#### New episodes or errors

We see that we have 3 episodes that can be new episodes with wrong code (reusing the code). All episodes
don't intersect with old polygons and 1 of them has new species:

+ Code reuse cases:
  
  - "22-001": More than 5km of difference, its clear is a new episode, so we change the code in past episodes
  - "22-002": More than 2km of difference, its clear is a new episode, so we change the code in past episodes
  - "28-001": More than 17km of difference, its clear is a new episode, so we change the code in past episodes
  
  
  All this episodes are setted as new episodes, but they only stay in the database if they fulfill the
  expectations for new episodes (mortality, affectation and area thresholds)
  
```{r code_reuse_plots_2018}
create_polygon_plot('22-001', data_dirty_2018, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2018))
create_polygon_plot('22-002', data_dirty_2018, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2018))
create_polygon_plot('28-001', data_dirty_2018, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2018))
```
  

```{r error_or_new_2018_fix}
data_dirty_2018_error_fixed <-
  data_dirty_2018_error %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        "22-001", "22-002", "28-001"
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  }
  

# update clean data from pervious years
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::mutate(
    original_episode_id = episode_id,
    episode_id = dplyr::if_else(
      episode_id %in% c(
        "22-001", "22-002", "28-001"
      ),
      glue::glue("{episode_id}-2017"),
      episode_id
    )
  )
```

## Clean data for 2018

Finally we have the clean data for 2018:

```{r data_clean_2018}
data_clean_2018 <- list(
  data_dirty_2018_ok, data_dirty_2018_duplicated_species_fixed,
  data_dirty_2018_new_species_populus_fixed, data_dirty_2018_new_species_others_fixed,
  data_dirty_2018_error_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2018 clean data.

```{r deboscat_update_2018}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2018) %>%
  dplyr::arrange(episode_id, year)
```

# 2019 data

We repeat the process for 2019 data:

```{r data_2019_process}
data_dirty_2019 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2019) %>%
  dplyr::distinct() %>%
  {
    data_raw_2019 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2019 data checks

```{r data_2019_checks}
data_dirty_2019_checks <- data_dirty_2019 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat %>% dplyr::filter(episode_area > 0)) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2019 <- data_dirty_2019_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2019
```

### Custom cleaning

Now we have an idea about how the 2019 episodes behave (**wow, no duplicated species this year!!**).
Let's make the round of custom cleanings:

```{r data_2019_problems}
data_dirty_2019_ok <- data_dirty_2019_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2019_new_species_populus <- data_dirty_2019_checks %>%
  dplyr::filter(check_meaning == 'New species Populus nigra')

data_dirty_2019_new_species_others <- data_dirty_2019_checks %>%
  dplyr::filter(check_meaning == 'New species others')
```

#### New species, being *Populus nigra*

When we have *Populus nigra* as a new species, we must check that is not really a *Pinus nigra* in
disguise. We have 3 episodes with this species as new:

  - "06-038", "06-048" and "25-022" are all mistakes, they should be *Pinus nigra*

```{r new_species_populus_2019}
data_dirty_2019_new_species_populus_fixed <-
  data_dirty_2019_new_species_populus %>%
  dplyr::ungroup() %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    function(episode_data, episode_name) {
      if (episode_name %in% c("06-038", "06-048", "25-022")) {
        res <- episode_data %>%
          dplyr::mutate(species_id = if_else(species_id == 'Populus nigra', 'Pinus nigra', species_id))
      } else {
        res <- episode_data
      }
      return(res)
    }
  )

```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2019}
data_dirty_2019_new_species_others_fixed <-
  data_dirty_2019_new_species_others
```

## Clean data for 2019

Finally we have the clean data for 2019:

```{r data_clean_2019}
data_clean_2019 <- list(
  data_dirty_2019_ok,
  data_dirty_2019_new_species_populus_fixed, data_dirty_2019_new_species_others_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2019 clean data.

```{r deboscat_update_2019}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2019) %>%
  dplyr::arrange(episode_id, year)
```

# 2020 data

We repeat the process for 2020 data:

```{r data_2020_process}
data_dirty_2020 <- data_dirty_2014_2020 %>%
  dplyr::filter(year == 2020) %>%
  dplyr::distinct() %>%
  {
    data_raw_2020 <<- .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2020 data checks

```{r data_2020_checks}
data_dirty_2020_checks <- data_dirty_2020 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat %>% dplyr::filter(episode_area > 0)) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2020 <- data_dirty_2020_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2020
```

### Custom cleaning

Now we have an idea about how the 2020 episodes behave.
Let's make the round of custom cleanings:

```{r data_2020_problems}
data_dirty_2020_ok <- data_dirty_2020_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2020_duplicated_species <- data_dirty_2020_checks %>%
  dplyr::filter(check_meaning == 'Duplicated species')

data_dirty_2020_new_species_others <- data_dirty_2020_checks %>%
  dplyr::filter(check_meaning == 'New species others')
```

#### Duplicated species

We have 1 episodes with duplicated species:

  - "06-024": Two sets of species, the only difference is the polygon and it makes sense the
  bigger polygon, as it is in concordance with the previous years.

```{r duplicated_species_fix_2020}
data_dirty_2020_duplicated_species_fixed <-
  data_dirty_2020_duplicated_species %>%
  split(.$episode_id) %>%
  purrr::imap_dfr(
    .f = function(episode_data, episode_name) {
      if (episode_name == '06-024') {
        res <- episode_data %>%
          dplyr::filter(episode_area == max(episode_area))
      }
      return(res)
    }
  )
```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2020}
data_dirty_2020_new_species_others_fixed <-
  data_dirty_2020_new_species_others
```

## Clean data for 2020

Finally we have the clean data for 2020:

```{r data_clean_2020}
data_clean_2020 <- list(
  data_dirty_2020_ok,
  data_dirty_2020_duplicated_species_fixed, data_dirty_2020_new_species_others_fixed
) %>%
  dplyr::bind_rows() %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2020 clean data.

```{r deboscat_update_2020}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2020) %>%
  dplyr::arrange(episode_id, year)
```

# 2021 data

We repeat the process for 2021 data

```{r data_2021_process}
data_dirty_2021 <- data_dirty_2021 %>%
  dplyr::filter(year == 2021) %>%
  dplyr::distinct() %>%
  {
    data_raw_2021 <<- .
    .
  } %>%
  create_data_dirty(data_dirty_deboscat)

#### MANUAL CHANGE!!!!!!!! This have been forced by Mireia and Jordi, to add this episode
data_dirty_2021 <- data_dirty_2021 %>%
  dplyr::bind_rows(
    data_raw_2021 %>%
      dplyr::filter(episode_id == "40-019") %>%
      dplyr::mutate(new_episode = TRUE)
  )
```

## 2021 data checks

```{r data_2021_checks}
data_dirty_2021_checks <- data_dirty_2021 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat %>% dplyr::filter(episode_area > 0)) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2021 <- data_dirty_2021_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2021
```


### Custom cleaning

Now we have an idea about how the 2021 episodes behave. Let's make the round of custom cleanings:

```{r data_2021_problems}
data_dirty_2021_ok <- data_dirty_2021_checks %>%
  dplyr::filter(check_meaning %in% c('Ok'))

data_dirty_2021_new_species_others <- data_dirty_2021_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2021_error <- data_dirty_2021_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### New species, no *Populus nigra*

When we have new species but none of them are *Populus nigra* so we are gonna assume is ok.

```{r new_species_others_fix_2021}
data_dirty_2021_new_species_others_fixed <-
  data_dirty_2021_new_species_others
```

#### New episodes or errors

We see that we have 3 episodes that can be new episodes with wrong code (reusing the code). All episodes
don't intersect with old polygons:

+ Code reuse cases:
  
  - "13-001": More than 6km of difference, its clear is a new episode, so we change the code in past episodes
  - "21-031": More than 65km of difference, its clear is a new episode, so we change the code in past episodes
  - "34-056": More than 35km of difference, its clear is a new episode, so we change the code in past episodes
  
All this episodes are setted as new episodes, but they only stay in the database if they fulfill the
expectations for new episodes (mortality, affectation and area thresholds)
  
```{r code_reuse_plots_2021}
create_polygon_plot('13-001', data_dirty_2021, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2021))
create_polygon_plot('21-031', data_dirty_2021, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2021))
create_polygon_plot('34-056', data_dirty_2021, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2021))
```

```{r error_or_new_2021_fix}
data_dirty_2021_error_fixed <-
  data_dirty_2021_error %>%
  # new episodes must be checked as new
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        "13-001", "21-031", "34-056"
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  }
  

# update clean data from pervious years
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::mutate(
    original_episode_id = episode_id,
    episode_id = dplyr::if_else(
      episode_id %in% c(
        "13-001", "21-031", "34-056"
      ),
      glue::glue("{episode_id}-2020"),
      episode_id
    )
  )
```

## Clean data for 2021

Finally we have the clean data for 2021:

```{r data_clean_2021}
data_clean_2021 <- list(
  data_dirty_2021_ok, data_dirty_2021_new_species_others_fixed, data_dirty_2021_error_fixed
) %>%
  #### fix problems detected on data checks post cleaning when all dates are
  dplyr::bind_rows() %>%
  #### processed
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == "04-033", "04-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "23-010", "23-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "23-011", "23-101", episode_id
    ),
    new_episode = dplyr::if_else(
      episode_id %in% c(
      "04-100", "23-100", "23-101"
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  } %>%
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2021 clean data.

```{r deboscat_update_2021}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2021) %>%
  dplyr::arrange(episode_id, year)
```

# 2022 data

We repeat the process for 2022 data

```{r data_2022_process}
data_dirty_2022 <- data_dirty_2022 %>%
  dplyr::filter(year == 2022) %>%
  dplyr::distinct() %>%
  {
    data_raw_2022 <<- .
    .
  } %>%
  create_data_dirty(data_dirty_deboscat)
```

## 2022 data checks

```{r data_2022_checks}
data_dirty_2022_checks <- data_dirty_2022 %>%
  split(.$episode_id) %>%
  purrr::map(.f = check_species, old_episodes_data = data_dirty_deboscat) %>%
  purrr::map(.f = check_polygons, old_episodes_data = data_dirty_deboscat %>% dplyr::filter(episode_area > 0)) %>%
  dplyr::bind_rows() %>%
  check_error_meaning()

summary_checks_2022 <- data_dirty_2022_checks %>%
  dplyr::group_by(check_duplicated_species, check_new_species, check_polygon_intersects,
           check_polygon_distance_above_1000, check_old_polygon_intersects, check_meaning) %>%
  dplyr::summarise(
    rows = dplyr::n(),
    episodes = dplyr::n_distinct(episode_id),
    check_meaning = dplyr::first(check_meaning)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(check_meaning) %>%
  dplyr::summarise(
    rows = sum(rows),
    episodes = sum(episodes)
  )

summary_checks_2022
```

### Custom cleaning

Now we have an idea about how the 2022 episodes behave. Let's make the round of custom cleanings:

```{r data_2022_problems}
data_dirty_2022_ok <- data_dirty_2022_checks %>%
  dplyr::filter(check_meaning %in% c('Ok', 'Ok / New species others'))

data_dirty_2022_new_species_others <- data_dirty_2022_checks %>%
  dplyr::filter(check_meaning == 'New species others')

data_dirty_2022_error <- data_dirty_2022_checks %>%
  dplyr::filter(check_meaning == 'New or error')
```

#### New species, no *Populus nigra*

All seem like new species correctly added.

```{r new_species_others_fix_2022}
data_dirty_2022_new_species_others_fixed <-
  data_dirty_2022_new_species_others
```

#### New episodes or errors

We see that we have 2 episodes that can be new episodes with wrong code (reusing the code). All episodes
don't intersect with old polygons:

+ Same episodes (distances below 5 km)

  - "05-002" and "31-005": same episodes after 4 years. We need to assign
  new codes.
  
```{r code_reuse_plots_2022}
create_polygon_plot('05-002', data_dirty_2022, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2022))
create_polygon_plot('31-005', data_dirty_2022, data_dirty_deboscat, data_dirty_2014_2020 %>% filter(year > 2022))
```

All this episodes are maintained as they are.

```{r error_or_new_2022_fix}
data_dirty_2022_error_fixed <-
  data_dirty_2022_error |>
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == "05-002" & year %in% c(2022),
      "05-012",
      episode_id
    )
  ) |>
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == "31-005" & year %in% c(2022),
      "31-040",
      episode_id
    )
  ) |>
  dplyr::mutate(
    new_episode = dplyr::if_else(
      episode_id %in% c(
        "31-040", "05-012"
      ),
      TRUE,
      new_episode
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  }

```

## Clean data for 2022

Finally we have the clean data for 2022:

```{r data_clean_2022}
data_clean_2022 <- list(
  data_dirty_2022_ok, data_dirty_2022_new_species_others_fixed, data_dirty_2022_error_fixed
) %>%
  dplyr::bind_rows() %>%
  #### fix problems detected on data checks post cleaning when all dates are
  #### processed
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == "06-020", "06-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "13-004", "13-006", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "14-034", "14-101", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "14-007", "14-102", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "19-013", "19-120", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "24-032", "24-130", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "24-064", "24-133", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "24-073", "24-135", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "26-004", "26-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "26-005", "26-101", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "29-002", "29-010", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "29-005", "29-011", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "34-051", "34-101", episode_id
    ),
    new_episode = dplyr::if_else(
      episode_id %in% c(
        "06-100", "13-006", "14-101", "14-102", "19-120", "24-130", "24-133",
        "24-135", "26-100", "26-101", "29-010", "29-011", "34-101"
      ),
      TRUE,
      new_episode
    ),
    # mutates from 2021 not fixed that year (so no new episode)
    episode_id = dplyr::if_else(
      episode_id == "04-033", "04-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "23-010", "23-100", episode_id
    ),
    episode_id = dplyr::if_else(
      episode_id == "23-011", "23-101", episode_id
    )
  ) %>%
  # New episodes that start this year must go under the test
  {
    temp_data <- .
    ok_episodes <- temp_data %>%
      dplyr::filter(
      # 5% mortality or 40% affected
      mortality_perc >= 5 | (decoloration_perc + defoliation_perc) >= 50,
      # area more than 3 ha
      episode_area >= 3
    ) %>%
      dplyr::pull(episode_id) %>% 
      unique()
    
    temp_data %>%
      dplyr::filter(episode_id %in% ok_episodes | !new_episode)
  } %>%
  ####
  dplyr::arrange(episode_id, year, species_id) %>%
  dplyr::select(!starts_with('check'))
```

## Deboscat data

We need to update `data_dirty_deboscat` to store the 2021 clean data.

```{r deboscat_update_2022}
data_dirty_deboscat <- data_dirty_deboscat %>%
  dplyr::bind_rows(data_clean_2022) %>%
  dplyr::arrange(episode_id, year)
```


# Data post-cleaning

## Deciduous *Quercus*, spatial county assignation

All deciduous oaks (*Quercus cerroides*, *Quercus faginea* and *Quercus humilis*) must be blended in the same
category. In case of several deciduous oaks in the same episode/year combination, their values are aggregated.

And finally we assign the county to which each episode polygon belongs. We do this in two ways, first we assign
which county covers the episode polygon, second we assign which county covers the episode centroid. That way
we can check later if there is concordance between them and with the county code in the `episode_id`

```{r data_muddy}
data_muddy_deboscat <-
  data_dirty_deboscat %>%
  dplyr::group_by(episode_id, year) %>%
  ## Quercus normalization
  dplyr::group_modify(
    .f = function(year_data, year_data_keys) {
      year_data %>%
        dplyr::mutate(
          species_id = if_else(
            species_id %in% c('Quercus cerroides', 'Quercus faginea', 'Quercus humilis'),
            'Deciduous oaks', species_id
          )
        ) %>% {
          if (length(which(.$species_id == 'Deciduous oaks')) > 1) {
            temp_res <- .
            temp_res %>%
              dplyr::group_by(species_id) %>%
              dplyr::summarise(
                geometry = sf::st_sfc(dplyr::first(year_data$geometry)),
                episode_area = dplyr::first(episode_area),
                new_episode = dplyr::first(new_episode),
                affected_trees_distribution = dplyr::first(affected_trees_distribution),
                affected_trees_perc = sum(cover_perc*affected_trees_perc)/sum(cover_perc),
                decoloration_perc = sum(cover_perc*decoloration_perc)/sum(cover_perc),
                defoliation_perc = sum(cover_perc*defoliation_perc)/sum(cover_perc),
                mortality_perc = sum(cover_perc*mortality_perc)/sum(cover_perc),
                cover_perc = if_else(sum(cover_perc) > 100, 100, sum(cover_perc))
              )
          } else {
            .
          }
        }
    }
  ) %>%
  ## County spatial assignation
  sf::st_as_sf() %>%
  {
    data_muddy_deboscat_crs <<- sf::st_crs(.)
    .
  } %>%
  sf::st_join(
    counties_sf %>%
      sf::st_transform(crs = sf::st_crs(data_muddy_deboscat_crs)),
    join = sf::st_covered_by
  ) %>%
  ## variables needed for checks
  dplyr::mutate(
    original_county_id = stringr::str_sub(episode_id, 1, 2),
    original_county_name = original_county_id %>%
      purrr::map_chr(.f = ~ counties_sf$spatial_county_name[which(counties_sf$spatial_county_id == .x)]),
    polygon_centroid = sf::st_centroid(geometry)
  ) %>% {
    centroid_sf <- .
    centroid_sf %>%
      sf::st_set_geometry(centroid_sf$polygon_centroid) %>%
      dplyr::select(!dplyr::starts_with('spatial')) %>%
      sf::st_join(
        counties_sf %>%
          sf::st_transform(crs = sf::st_crs(centroid_sf)),
        join = sf::st_covered_by
      ) %>%
      dplyr::as_tibble() %>%
      dplyr::select(
        episode_id, year, species_id,
        centroid_county_id = spatial_county_id, centroid_county_name = spatial_county_name
      ) %>%
      dplyr::right_join(centroid_sf)
  } %>%
  dplyr::select(
    dplyr::everything(), dplyr::ends_with('county_name'), dplyr::ends_with('county_id'),
    geometry, polygon_centroid
  )
  
```

##



## Data checks

We are gonna check the following:

  1. Check if county spatial assignation coincides with code county assignation.
  1. Check for episodes that intersect with other episodes. Here we check episodes that intersect, centroids
  are less than 3km from other episodes and centroids intersects with other episodes. This will give us an
  idea of possible errors in episode codes o episodes that are the same but are coded two or more times.


```{r data_muddy_deboscat}
# spatial checks
data_muddy_episodes_intersection <- data_muddy_deboscat %>%
  dplyr::ungroup() %>%
  dplyr::select(episode_id, year, geometry, polygon_centroid) %>%
  dplyr::distinct() %>%
  {
    data_muddy_episode_year_vec <<- dplyr::pull(., episode_id)
    data_muddy_episode_year_unique <<- .
    
    data_muddy_episodes_under_3000 <<- sf::st_is_within_distance(
      data_muddy_episode_year_unique$polygon_centroid, data_muddy_episode_year_unique$geometry,
      3000
    ) %>%
      purrr::map(
        .f = ~ data_muddy_episode_year_vec[.x] %>% unique()
      ) %>% 
      purrr::set_names(
        glue::glue("{data_muddy_episode_year_unique$episode_id}-{data_muddy_episode_year_unique$year}")
      ) %>%
      purrr::keep(.p = function(x) {length(x) > 1})
    
    data_muddy_episodes_centroids_intersection <<- sf::st_intersects(
      data_muddy_episode_year_unique$polygon_centroid, data_muddy_episode_year_unique$geometry
    ) %>%
      purrr::map(
        .f = ~ data_muddy_episode_year_vec[.x] %>% unique()
      ) %>% 
      purrr::set_names(
        glue::glue("{data_muddy_episode_year_unique$episode_id}-{data_muddy_episode_year_unique$year}")
      ) %>%
      purrr::keep(.p = function(x) {length(x) > 1}) %>%
      magrittr::extract(!duplicated(.))
    .
  } %>% 
  sf::st_as_sf() %>%
  sf::st_cast('MULTIPOLYGON') %>%
  sf::st_intersects() %>%
  purrr::map(
    .f = ~ data_muddy_episode_year_vec[.x] %>% unique()
  ) %>%
  purrr::set_names(
    glue::glue("{data_muddy_episode_year_unique$episode_id}-{data_muddy_episode_year_unique$year}")
  ) %>%
  purrr::keep(.p = function(x) {length(x) > 1})

# build all the checks in an object
data_muddy_deboscat_checks <-
  data_muddy_deboscat %>%
  dplyr::left_join(
    tibble::enframe(data_muddy_episodes_centroids_intersection) %>%
      tidyr::separate(name, c('episode_id', 'year'), sep = -5) %>%
      dplyr::mutate(year = as.numeric(stringr::str_remove(year, '-'))) %>%
      dplyr::rename(check_centroid_intersections = value),
    by = c('episode_id', 'year')
  ) %>%
  dplyr::group_by(episode_id, year, species_id) %>%
  dplyr::mutate(
    # county checks
    check_county_all = !(spatial_county_id == original_county_id & centroid_county_id == original_county_id),
    check_county_centroid = !centroid_county_id == original_county_id,
    check_county_spatial = !spatial_county_id == original_county_id,
    check_county = !(!any(check_county_all, check_county_centroid, check_county_spatial, na.rm = TRUE)),
    check_county_meaning = dplyr::case_when(
      isFALSE(check_county) ~ 'Ok',
      isTRUE(check_county) ~ 'Incorrect county in episode ID',
      TRUE ~ rlang::na_chr
    ),
    check_centroid_intersections_meaning = purrr::map_chr(
      check_centroid_intersections,
      .f = function(intersections) {
        if (rlang::is_null(intersections)) {
          return('Ok')
        } else {
          return('Centroid intersects with another episode')
        }
      }
    )
  )

data_muddy_deboscat_checks
```


First, we are gonna check the episodes that have their centroid inside other episodes:

```{r}
data_muddy_deboscat_checks %>%
  dplyr::filter(check_centroid_intersections_meaning == 'Centroid intersects with another episode')

data_muddy_episodes_centroids_intersection
```

So, we go one by one :(


### Fixes


```{r data_muddy_centroid_intersections_cleaning}
data_muddy_deboscat_centroids <-
  data_muddy_deboscat %>%
  dplyr::filter(episode_id != '02-010-2015') %>%
  dplyr::filter(!(episode_id == '04-036' & year == 2017)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '04-005' & year %in% c(2017,2018), glue::glue('04-036'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '04-031' & year %in% c(2016,2017,2018), glue::glue('04-026'), episode_id
    )
  ) %>%
  dplyr::filter(episode_id != '04-038') %>%
  {
    temp <- .
    temp %>%
      dplyr::filter(episode_id %in% c('06-006', '06-007'), year == 2012) %>%
      dplyr::group_by(species_id) %>%
      dplyr::summarise(
        geometry = sf::st_union(geometry),
        dplyr::across(dplyr::ends_with('_perc'), ~ mean(.x, na.rm = TRUE))
      ) -> temp_fixed

    temp %>%
      dplyr::filter(episode_id != '06-007') %>%
      dplyr::mutate(
        geometry = dplyr::if_else(
          episode_id == '06-006' & year %in% c(2012), temp_fixed$geometry[1] %>% sf::st_cast('GEOMETRY'), geometry
        ),
        episode_area = dplyr::if_else(
          episode_id == '06-006' & year %in% c(2012), as.numeric(sf::st_area(geometry))/10000, episode_area
        )
      )
  } %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '07-026' & year %in% c(2020, 2021, 2022), glue::glue('07-019'), episode_id
    )
  ) %>%
  {
    # spatial changes
    temp_data <- .
  
    poly_04 <- temp_data[which(temp_data$episode_id == '10-004' & temp_data$year == 2015), 'geometry'][[1]][1]
    poly_05 <- temp_data[which(temp_data$episode_id == '10-005' & temp_data$year == 2015), 'geometry'][[1]][1]
  
    poly_04_minus_05 <- sf::st_difference(sf::st_make_valid(poly_04), sf::st_make_valid(poly_05))
    sf::st_centroid(poly_04_minus_05)
    # there is still a small portion that must be removed
    poly_10_04_fixed <<- sf::st_intersection(poly_04_minus_05, sf::st_buffer(sf::st_centroid(poly_04_minus_05), 1500))
    
    poly_43 <- temp_data[which(temp_data$episode_id == '06-043' & temp_data$year == 2017), 'geometry'][[1]][1]
    poly_20 <- temp_data[which(temp_data$episode_id == '06-020' & temp_data$year == 2017), 'geometry'][[1]][1]
  
    poly_43_minus_20 <- sf::st_difference(poly_43, poly_20)
    sf::st_centroid(poly_43_minus_20)
    # there is still a small portion that must be removed
    poly_06_043_fixed <<- sf::st_intersection(poly_43_minus_20, sf::st_buffer(sf::st_centroid(poly_43_minus_20), 1000))
    
    temp_data %>%
      dplyr::mutate(
        geometry = dplyr::case_when(
          episode_id == '06-043' & year == 2017 ~ sf::st_cast(poly_06_043_fixed, 'GEOMETRY'),
          episode_id == '10-004' & year == 2015 ~ sf::st_cast(poly_10_04_fixed, 'GEOMETRY'),
          TRUE ~ geometry
        )
      )
  } %>%
  dplyr::filter(episode_id != '10-040') %>%
  dplyr::filter(episode_id != '10-046') %>%
  dplyr::filter(!(episode_id == '16-002' & year == 2014)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '20-012-2012' & year %in% c(2012), glue::glue('20-005'), episode_id
    )
  ) %>% 
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '21-031-2020' & year %in% c(2018), glue::glue('24-031'), episode_id
    )
  ) %>% 
  dplyr::filter(!(episode_id == '38-002' & year == 2012)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '38-002' & year %in% c(2015), glue::glue('23-002'), episode_id
    )
  ) %>%
  # dplyr::mutate(
  #   episode_id = dplyr::if_else(
  #     episode_id == '23-010' & year %in% c(2021, 2022), glue::glue('23-011'), dplyr::if_else(
  #     episode_id == '23-011' & year %in% c(2021, 2022), glue::glue('23-010'), episode_id
  #   )
  #   )
  # ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-001' & year %in% c(2012), glue::glue('24-032'), episode_id
    )
  ) %>% 
  dplyr::filter(!(episode_id == '24-106' & year == 2019)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-016' & year %in% c(2019), glue::glue('24-106'), episode_id
    )
  ) %>% 
  dplyr::filter(!(episode_id == '24-043' & year == 2012)) %>% 
  dplyr::filter(!(episode_id == '24-073-2015' & year == 2013)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '25-037-2016' & year %in% c(2016), glue::glue('25-029'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '27-001' & year %in% c(2017), glue::glue('28-001'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '31-001-2012' & year %in% c(2012), glue::glue('31-007-2015'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '31-007-2012' & year %in% c(2012), glue::glue('31-001-2015'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '31-002-2012' & year %in% c(2012), glue::glue('31-008-2016'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '31-008-2012' & year %in% c(2012), glue::glue('31-002-2015'), episode_id
    )
  ) %>%
  dplyr::filter(!(episode_id == '32-011' & year == 2014)) %>%
  # dplyr::mutate(
  #   episode_id = dplyr::if_else(
  #     episode_id == '32-001' & year %in% c(2017, 2018, 2019), glue::glue('32-002-2020'), episode_id
  #   )
  # ) %>%
  dplyr::filter(!(episode_id == '32-013' & year == 2019)) %>%
  dplyr::filter(!(episode_id == '35-012' & year == 2012)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '36-032' & year %in% c(2016), glue::glue('35-032'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '40-003-2012' & year %in% c(2012), glue::glue('40-006'), episode_id
    )
  ) %>%
  dplyr::filter(!(episode_id == '40-005' & year == 2012)) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '31-005' & year %in% c(2022), glue::glue('31-009'), episode_id
    )
  ) %>%
  dplyr::filter(!(episode_id == '02-038' & year == 2022)) %>%
  dplyr::filter(!(episode_id == '14-013' & year %in% c(2020, 2021, 2022))) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '14-066' & year %in% c(2020, 2021, 2022), glue::glue('14-013'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '14-078' & year %in% c(2017:2020), glue::glue('14-059'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-035' & year %in% c(2017:2022), glue::glue('24-131'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-039' & year %in% c(2021:2022), glue::glue('24-132'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-048' & year %in% c(2017:2019), glue::glue('24-200'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-060' & year %in% c(2017:2019), glue::glue('24-201'), episode_id
    )
  ) %>%
  dplyr::mutate(
    episode_id = dplyr::if_else(
      episode_id == '24-032' & year %in% c(2017:2019), glue::glue('24-202'), episode_id
    )
  )

###### Fix repeated codes in general
lag_check <- function(episode_data, keys) {
  episode_data |>
    dplyr::mutate(year_lag = dplyr::lag(year), difference = year - year_lag) |>
    dplyr::filter(difference > 2)
}

episode_with_lags <-
  data_muddy_deboscat_centroids |>
  dplyr::as_tibble() |>
  dplyr::select(episode_id, year) |>
  dplyr::distinct() |>
  dplyr::group_by(episode_id) |>
  dplyr::group_modify(.f = lag_check) |>
  dplyr::arrange(year, episode_id) |>
  dplyr::mutate(
    old_episode_id = glue::glue("{episode_id}-{year_lag}")
  )

episode_id_mutate_exprs <- episode_with_lags |>
  dplyr::mutate(
    expr_mutate = glue::glue(
      "dplyr::if_else(
         episode_id == '{.data$episode_id}' & year < {.data$year}, '{.data$old_episode_id}', episode_id
       )"
    )
  ) |>
  dplyr::pull(expr_mutate) |>
  rlang::parse_exprs()

new_episode_mutate_exprs <- episode_with_lags |>
  # dplyr::group_by(episode_id) |>
  # dplyr::summarise(year = max(year)) |>
  dplyr::mutate(
    expr_mutate = glue::glue(
      "dplyr::if_else(
       episode_id == '{.data$episode_id}' & year == {.data$year}, TRUE, new_episode
     )"
    )
  ) |>
  dplyr::pull(expr_mutate) |>
  rlang::parse_exprs()

new_episode_mutate_exprs |>
  purrr::walk(
    .f = \(mutate_expr) {
      data_muddy_deboscat_centroids <<- data_muddy_deboscat_centroids |>
        dplyr::mutate(new_episode = !! mutate_expr)
    }
  )

episode_id_mutate_exprs |>
  purrr::walk(
    .f = \(mutate_expr) {
      data_muddy_deboscat_centroids <<- data_muddy_deboscat_centroids |>
        dplyr::mutate(episode_id = !! mutate_expr)
    }
  )

data_muddy_deboscat_centroids |>
  dplyr::filter(stringr::str_detect(episode_id, "14-056")) |>
  View()
```

### Checks

See `data_muddy_episodes_centroids_checks.Rmd`

# Final data

Now we have the data as much clean as we can. We need to codify again the new episodes (this last step
of centroids can mess with the new/old classification), cast all geometries as multipolygons, and create the
sf. Also, fix the county assignation.

We also create the cicatrization index for each site/year combination, with the following formula:

$$
\frac{\sum_{sp=1}^{sp} (cover_{sp}*affectation_{sp})}{\sum_{sp=1}^{sp} cover_{sp}}
$$


```{r final_data}
data_clean_deboscat <- data_muddy_deboscat_centroids %>%
  split(.$episode_id) %>%
  purrr::map_dfr(
    .f = function(episode_data) {
      episode_data %>%
        dplyr::mutate(
          new_episode = dplyr::case_when(
            year == 2012 ~ new_episode,
            TRUE ~ if_else(year == min(year), TRUE, FALSE)
          ),
          county_name = dplyr::if_else(is.na(spatial_county_name), centroid_county_name, spatial_county_name),
          county_id = dplyr::if_else(is.na(spatial_county_id), centroid_county_id, spatial_county_id)
        )
    }
  ) %>%
  dplyr::group_by(episode_id, year) %>% 
  ## Cicatrization index
  dplyr::mutate(
    cicatrization_index = sum(cover_perc*affected_trees_perc)/sum(cover_perc)
  ) %>%
  dplyr::select(
    episode_id, year, species_id, dplyr::starts_with('county'), dplyr::ends_with('perc'), episode_area,
    new_episode, affected_trees_distribution, cicatrization_index, geometry
  ) %>%
  dplyr::ungroup() %>%
  sf::st_as_sf() %>%
  sf::st_cast('MULTIPOLYGON')
```

Let's save the clean data:

```{r}
readr::write_csv(data_clean_deboscat, 'deboscat_table.csv')
sf::st_write(data_clean_deboscat, 'deboscat_table.gpkg', delete_dsn = TRUE)
save.image('deboscat_process_objects.RData')
```


# Appendix A. Cicatrization index tendencies

```{r, echo=FALSE}
data_clean_deboscat %>%
  dplyr::as_tibble() %>%
  dplyr::select(episode_id, year, cicatrization_index) %>%
  dplyr::distinct() %>%
  dplyr::group_by(episode_id) %>%
  dplyr::mutate(
    year_normalized = seq(1:n()),
    panel = max(year_normalized)
  ) %>%
  ggplot(aes(x = year_normalized, y = cicatrization_index)) +
  geom_line(aes(colour = episode_id), show.legend = FALSE, alpha = 0.1) +
  geom_boxplot(aes(group = year_normalized), show.legend = FALSE) +
  stat_smooth(show.legend = FALSE, method = 'lm', color = 'black', size = 1, se = TRUE) +
  # facet_grid(rows = vars(panel))
  facet_wrap(vars(panel)) +
  scale_x_continuous(breaks = 1:9) +
  labs(
    title = 'Cicatrization index tendency',
    subtitle = 'by number of years recorded for each episode',
    caption = 'Panels are numer of years recorded for the episodes'
  )

data_clean_deboscat %>%
  dplyr::as_tibble() %>%
  dplyr::select(episode_id, year, cicatrization_index) %>%
  dplyr::distinct() %>%
  dplyr::group_by(episode_id) %>%
  dplyr::mutate(
    year_normalized = seq(1:n()),
    panel = max(year_normalized)
  ) %>%
  ggplot(aes(x = year, y = cicatrization_index)) +
  geom_line(aes(colour = episode_id), show.legend = FALSE, alpha = 0.1) +
  geom_boxplot(aes(group = year), show.legend = FALSE) +
  stat_smooth(show.legend = FALSE, method = 'lm', color = 'black', size = 1, se = TRUE) +
  # facet_grid(rows = vars(panel))
  facet_wrap(vars(panel)) +
  labs(
    title = 'Cicatrization index tendency',
    subtitle = 'grouped by year',
    caption = 'Panels are numer of years recorded for the episodes'
  )
```

# Appendix B. Episodes

```{r, fig.width=12, fig.height=10, eval=TRUE}
diagnostic_plots <- data_clean_deboscat %>%
  split(.$episode_id) %>%
  purrr::map(
    .f = ~ episode_diagnostic_plot(.x)
  )

diagnostic_plots
```

